Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-04 paper.qmd
Added error plot for MNSIT data

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("a")

@@

```{r}
#| fig-width: 25
#| fig-height: 5

nldr_mnist1 + nldr_mnist2 + 
  nldr_mnist3 + nldr_mnist4 + nldr_mnist5 +
  plot_layout(ncol = 5)
```

>>>>

nldr_mnist1 <- tsne_mnist |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#ff7f00') +
  interior_annotation("a", c(0.08, 0.93))

@@

```{r}
#| label: combine-data-mnist

error_mnist_umap <- read_rds("data/mnist/error_mnist_umap.rds")
error_mnist_tsne <- read_rds("data/mnist/error_mnist_tsne.rds")
error_mnist_phate <- read_rds("data/mnist/error_mnist_phate.rds")
error_mnist_trimap <- read_rds("data/mnist/error_mnist_trimap.rds")
error_mnist_pacmap <- read_rds("data/mnist/error_mnist_pacmap.rds")

error_mnist <- bind_rows(error_mnist_umap, 
                        error_mnist_tsne,
                        error_mnist_phate,
                        error_mnist_trimap,
                        error_mnist_pacmap)

error_mnist <- error_mnist |>
  mutate(a1 = round(a1, 2)) |>
  filter(bin1 >= 5) |>
  group_by(method, a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()
```

```{r}
#| label: error-comp-mnist

error_plot_mnist <- ggplot(error_mnist, 
                          aes(x = a1, 
                              y = MSE, 
                              colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_mnist$a1))[seq(1, length(unique(error_mnist$a1)), by = 5)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8','#4daf4a', "#ff7f00",'#a65628')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| fig-cap: ""
#| label: fig-mnist-mse
#| fig-pos: H
#| out-height: 100%

free(error_plot_mnist) + wrap_plots(nldr_mnist1, nldr_mnist2, nldr_mnist3, 
                                    nldr_mnist4, nldr_mnist5, ncol = 2)
```
